### 2021-03-15 treatise-pdflatex/4_simulation.tex
Slightly correct grammar
Chap 4: double check grammar

Let us represent complex vector and matrices by real vector and matrices.
For \m {\V {x} \in \mathbb {C} ^{M}}, define the real representation \m {\mathcal {R} \SB {\V {x}}} of \m {\V {x}} to be
%
\DispNum {R:x:R2:M1} {
\mathcal {R} \SB {\V {x}}
\in &\mathbb {R} ^{2M} \notag \\
\mathcal {R} \SB {\V {x}} _{\SB {m}}
= &\begin {cases}
\mathfrak {Re} \SB {\V {x} _{\SB {m'}}}, & m =2m' \\
\mathfrak {Im} \SB {\V {x} _{\SB {m'}}}, & m =2m'+1 \\
\end {cases} \notag \\
m' 
= &0, 1, 2, \ldots, M-1 
}
%
The injection is obvious, and we may define \m {\mathcal {R} ^{-1}} so that
%
\DispNum {R:1:x::x:} {
\mathcal {R} ^{-1} \SB {\mathcal {R} \SB {\V {x}}}
=\V {x} 
}
%
Accordingly, the following generalization to complex matrices is valid, once we call the ring representation of complex numbers.
For \m {\M {A} \in \mathbb {C} ^{M_1 \D M_2}}, define real representation \m {\mathcal {R} \SB {\M {A}}} of \m {\M {A}} to be
%
\DispNum {R:A:R2:21} {
\mathcal {R} \SB {\M {A}}
\in &\mathbb {R} ^{2M_1 \D 2M_2} \notag \\
\mathcal {R} \SB {\M {A}} _{\SB {m_1,m_2}}
= &\begin {cases}
\mathfrak {Re} \SB {\M {A} _{\SB {m_1',m_2'}}}, & \RB {m_1, m_2} = \RB {2m_1', 2m_2'} \\
\mathfrak {Im} \SB {\M {A} _{\SB {m_1',m_2'}}}, & \RB {m_1, m_2} = \RB {2m_1'+1, 2m_2'} \\
-\mathfrak {Im} \SB {\M {A} _{\SB {m_1',m_2'}}}, & \RB {m_1, m_2} = \RB {2m_1', 2m_2'+1} \\
\mathfrak {Re} \SB {\M {A} _{\SB {m_1',m_2'}}}, & \RB {m_1, m_2} = \RB {2m_1'+1, 2m_2'+1} \\
\end {cases} \notag \\
m_1 
= &0, 1, 2, \ldots, M_1 -1 \notag \\
m_2 
= &0, 1, 2, \ldots, M_2 -1 
}

@@

However, there is not simple way to determine the value of \m {\l} in advance.
We have tried basis pursuit denoising, with \m {\l = N_H^2 / \g_{\mathrm {DS}}} in the simulation.

@@

Denote the threshold for DS to be \m {\g_{\mathrm {DS}}}, and similar threshold of Lasso to be \m {\g_{\mathrm {Lasso}}}.
We set \m {\g_{\mathrm {DS}} = 2 \R {\log N_H}} as suggested in \cite {CaT07}.
For sake of comparison, \m {\g_{\mathrm {Lasso}} = 2 \R {\log N_H}} too.
For OMP, we consult Cai and Wang \cite {CaW11} for \m {\ell _2}-norm condition in their Theorem 7, and \m {\ell _\infty}-norm condition in their Theorem 8.
We take \m {\h_{\mathrm {OMP}} = 2 \R {\log N_H}} for \m {\infty}-norm condition, \m {\h_{\mathrm {OMP}} = \R {3} \SB {N_{B,r} N_{B,t}} ^ {1/4}} for 2-norm condition.
Particularly, in the plots of DS only or OMP only, we vary the values of \m {\g_{\mathrm {DS}}} and \m {\h_{\mathrm {OMP}}} by powers of \m {2}, to observe the effects of thresholds.
The maximal number of iteration of CVXPY is set to be \m {32}, and that of OMP is set to be \m {4 \R {N_{B,r} N_{B,t}}}.

@@

In the following, we plot the reciprocal of noise level vs relative error norm in log scale, for different values and ratios of \m {N_H = 6} over \m {N_{B,t}} and \m {N_{B,t}}.

@@

In the following, we plot the reciprocal of noise level vs relative error norm in log scale, for different values and ratios of \m {N_H = 12} over \m {N_{B,t}} and \m {N_{B,t}}.

@@

In the following, we plot the reciprocal of noise level vs relative error norm in log scale, for different values and ratios of \m {N_H = 18} over \m {N_{B,t}} and \m {N_{B,t}}.

@@

Suppose a linear program has \m {N} dimension variable and \m {M} inequality constraints, then the complexity is \m {\mathcal {O} \SB {N^2 M}}, assuming the Dantzig simplex method is used (\cite {BoV04}, p.6).
For our case, that would be \m {\mathcal {O} \SB {4 N_H ^4 \D 8 N_H^2} = \mathcal {O} \SB {N_H^6}}.
But other algorithms exist, where, in general, complexity of convex programs is difficult to analyze, as it is not easily to determine how many steps were calculated.

@@

Simulation illustrates that \m {t_{\mathrm {DS}}} grows tremendously with \m {N_H}, agreeing the criticism by Friedlander and Saunders \cite {FrS07} on the high complexity of DS.
It is not surprising, regarding the fact that the convex program has to find the Newton step by calculating \m {\M {P}}, a matrix of dimension \m {\M {N}_H^2}.
The matrix inversion is probably the bottleneck of complexity.
However, as we noted above, that different tolerance level of and maximal iteration number may result in vastly different computation time.

>>>>

Let us represent complex vectors and matrices by real vectors and matrices.
For \m {\V {x} \in \mathbb {C} ^{M}}, define the real representation \m {\mathcal {R} \SB {\V {x}}} of \m {\V {x}} to be
%
\DispNum {R:x:R2:M1} {
\mathcal {R} \SB {\V {x}}
\in &\mathbb {R} ^{2M} \notag \\
\mathcal {R} \SB {\V {x}} _{\SB {m}}
= &\begin {cases}
\mathfrak {Re} \SB {\V {x} _{\SB {m'}}}, & m =2m' \\
\mathfrak {Im} \SB {\V {x} _{\SB {m'}}}, & m =2m'+1 \\
\end {cases} \notag \\
m' 
= &0, 1, 2, \ldots, M-1 
}
%
The injection is obvious, and we may define \m {\mathcal {R} ^{-1}} so that
%
\DispNum {R:1:x::x:} {
\mathcal {R} ^{-1} \SB {\mathcal {R} \SB {\V {x}}}
=\V {x} 
}
%
Accordingly, the following generalization to complex matrices is valid, once we call the ring representation of complex numbers.
For \m {\M {A} \in \mathbb {C} ^{M_1 \D M_2}}, define real representation \m {\mathcal {R} \SB {\M {A}}} of \m {\M {A}} to be
%
\DispNum {R:A:R2:21} {
\mathcal {R} \SB {\M {A}}
\in &\mathbb {R} ^{2M_1 \D 2M_2} \notag \\
\mathcal {R} \SB {\M {A}} _{\SB {m_1,m_2}}
= &\begin {cases}
\mathfrak {Re} \SB {\M {A} _{\SB {m_1',m_2'}}}, & \RB {m_1, m_2} = \RB {2m_1', 2m_2'} \\
\mathfrak {Im} \SB {\M {A} _{\SB {m_1',m_2'}}}, & \RB {m_1, m_2} = \RB {2m_1'+1, 2m_2'} \\
-\mathfrak {Im} \SB {\M {A} _{\SB {m_1',m_2'}}}, & \RB {m_1, m_2} = \RB {2m_1', 2m_2'+1} \\
\mathfrak {Re} \SB {\M {A} _{\SB {m_1',m_2'}}}, & \RB {m_1, m_2} = \RB {2m_1'+1, 2m_2'+1} \\
\end {cases} \notag \\
m_1 
= &0, 1, 2, \ldots, M_1 -1 \notag \\
m_2 
= &0, 1, 2, \ldots, M_2 -1 
}

@@

However, there is no simple way to determine the value of \m {\l} in advance.
We have tried basis pursuit denoising, with \m {\l = N_H^2 / \g_{\mathrm {DS}}} in the simulation.

@@

Denote the threshold for DS to be \m {\g_{\mathrm {DS}}}, and similar threshold of Lasso to be \m {\g_{\mathrm {Lasso}}}.
We set \m {\g_{\mathrm {DS}} = 2 \R {\log N_H}} as suggested in \cite {CaT07}.
For sake of comparison, \m {\g_{\mathrm {Lasso}} = 2 \R {\log N_H}} too.
For OMP, we consult Cai and Wang \cite {CaW11} for \m {\ell _2}-norm condition in their Theorem 7, and \m {\ell _\infty}-norm condition in their Theorem 8.
We take \m {\h_{\mathrm {OMP}} = 2 \R {\log N_H}} for \m {\infty}-norm condition, \m {\h_{\mathrm {OMP}} = \R {3} \RB {N_{B,r} N_{B,t}} ^ {1/4}} for 2-norm condition.
The maximal number of iteration of CVXPY is set to be \m {32}, and that of OMP is set to be \m {4 \R {N_{B,r} N_{B,t}}}.

@@

In the following, we plot the reciprocal of noise level vs relative error norm in log scale, for different values and ratios of \m {N_H = 6} over \m {N_{B,t}} and \m {N_{B,r}}.

@@

In the following, we plot the reciprocal of noise level vs relative error norm in log scale, for different values and ratios of \m {N_H = 12} over \m {N_{B,t}} and \m {N_{B,r}}.

@@

In the following, we plot the reciprocal of noise level vs relative error norm in log scale, for different values and ratios of \m {N_H = 18} over \m {N_{B,t}} and \m {N_{B,r}}.

@@

Suppose a linear program has an \m {N} dimensional variable and \m {M} inequality constraints, then its complexity is \m {\mathcal {O} \SB {N^2 M}}, assuming the Dantzig simplex method is used (\cite {BoV04}, p.6).
For our case, that would be \m {\mathcal {O} \SB {4 N_H ^4 \D 8 N_H^2} = \mathcal {O} \SB {N_H^6}}.
But other algorithms exist, where, in general, complexity of convex programs is difficult to analyze, as it is not easily to determine how many steps were calculated.

@@

Simulation illustrates that \m {t_{\mathrm {DS}}} grows tremendously with \m {N_H}, agreeing Friedlander and Saunders \cite {FrS07} who noted the high complexity of DS.
This is not surprising, since the inversion of \m {\M {P} \M {P} ^\Adj} is probably the bottleneck of complexity, which has dimension \m {\M {N}_H^2}.
By the way, different tolerance levels and maximal iteration numbers may result in vastly different computation time.
